### 2025-02-27 Docs/article_spatio_temporal_life_change_in_daily_life_in_COVID19.tex
update file

\documentclass[paper={210mm,297mm},line_length=35zw,number_of_lines=31,head_space=30mm,gutter=40mm,baselineskip=2.0zw,headfoot_verticalposition=1.5zw]{jlreq}
%gutterを含んだレイアウトは要調整
\usepackage{luatexja}
\usepackage{graphicx}
\usepackage{float}

>>>>

\documentclass[paper={210mm,297mm},fontsize=15Q,line_length=35zw,number_of_lines=31,head_space=30mm,gutter=40mm,baselineskip=2.0zw,headfoot_verticalposition=1.5zw]{jlreq}
%gutterを含んだレイアウトは要調整
\usepackage{luatexja}
\usepackage{graphicx}
\usepackage{float}
